**First high-frequency time series of carbonate chemistry in the Arctic**

### 2022-03-29 awipev-CO2_presentation.Rmd
Conclusion added

>>>>

# **Conclusion**

- **First** high-frequency time series of the carbonate system in the Arctic 
- **Positive aspects**: 
  - Excellent support from AWIPEV staff but work overload
  - IPEV support secured for another 4-year period (2019-2022)
- **Logistical difficulties**:
  - Challenging environment; divers needed to sort out issues
  - Difficult and costly to gather a team and organize field trip at short notice
  - Winter sampling essential (once a month this season, more frequently would be more desirable)
  - Demanding for AWIPEV staff
  - IPEV does not cover the cost of analyses required for calibration (ca. 1000 €)
